---
title: "Marketing Spend and Customer Purchase Analysis"
author: "Yunhui Fan"
format:
  html:
    number-sections: true
    number-tables: true
    number-figures: true
  pdf:
    number-sections: true
    number-tables: true
    number-figures: true
---

# Load Libraries
```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
```

# Introduction
This report analyses customer data from an online retail marketing campaign.
It explores the relationship between per-customer marketing investment and purchase behaviour.
Understanding this link helps optimise future marketing resource allocation.
The findings provide data-driven insights for marketing strategy improvements.
# Research Question
Does higher marketing spend per customer lead to higher purchase amounts?
This analysis uses customer-level campaign data to test the direct relationship.
The result will validate the return of personalised marketing investments.
# Dataset Introduction
The dataset records customer-level metrics from a quarterly marketing campaign.
Key variables include marketing spend, site visits, customer segment, and purchase amount.
All missing values and invalid negative purchase records were removed for reliability.
The cleaned dataset ensures accurate and reproducible statistical analysis.
This data represents the official record of the campaign’s customer interactions.
```{r}
#| label: data-loading
#| echo: false
#| include: false

data <- read_csv("data/35036281_Yunhui Fan.csv")
data_clean <- data %>%
  drop_na() %>% 
  filter(purchase_amount >= 0)
```

## Dataset Description subsection
The cleaned dataset contains r nrow(data_clean) observations and r ncol(data_clean) variables.
Numeric variables include marketing spend, visits, and purchase amount, while customer segment is categorical.
Table @tbl-data-cleaning summarises the key numeric variables, and Figure @fig-purchaseplot shows the overall distribution of purchase amounts.

```{r}
#| label: tbl-data-cleaning
#| tbl-cap: "Summary of the dataset"
#| echo: false

data_clean %>%
  select(visits, marketing_spend, purchase_amount) %>%
  summary() %>%
  kable()
```

```{r}
#| label: fig-purchaseplot
#| fig-cap: "Distribution of customer purchase amounts."
#| echo: false
ggplot(data_clean, aes(x = purchase_amount)) +
  geom_histogram(fill = "steelblue", color = "white", bins = 15) +
  labs(x = "Purchase Amount (USD)", y = "Number of Customers")
```

## Results

The core research question examines whether higher marketing spend per customer leads to higher purchase amounts.
From Table @tbl-data-cleaning, we can see the central tendency and spread of marketing spend and purchase amounts.
As shown in Figure @fig-purchaseplot, most customers exhibit relatively moderate purchase values.
Figure @fig-marketing-purchase illustrates the relationship between marketing spend and purchase amount.
A clear positive trend is visible, indicating that increased marketing spend per customer is associated with higher purchase amounts.
The average purchase amount in the sample is r round(mean(data_clean$purchase_amount), 2) USD.
Together, Table @tbl-data-cleaning, Figure @fig-purchaseplot, and Figure @fig-marketing-purchase confirm that higher marketing investment per customer corresponds to greater customer spending.
This directly answers the research question with consistent visual and statistical evidence.
```{r}
#| label: fig-marketing-purchase
#| fig-cap: "Marketing spend vs customer purchase amount"
#| echo: false

ggplot(data_clean, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point(color = "darkblue", alpha = 0.6) +
  geom_smooth(method = lm, se = FALSE, color = "red") +
  labs(
    x = "Marketing Spend (USD)",
    y = "Purchase Amount (USD)"
  )
```


```{r}
#| label: fig-total-visits
#| fig-cap: "Distribution of customer visit frequencies"
#| echo: false

ggplot(data_clean, aes(x = visits)) +
  geom_bar(fill = "darkred", color = "black") +
  labs(
    x = "Number of Visits",
    y = "Count of Customers"
  )
```

Conclusion
The analysis clearly demonstrates that higher marketing spend per customer leads to higher purchase amounts.
The positive linear trend in Figure @fig-marketing-purchase validates the effectiveness of the campaign.
These results support increasing targeted marketing investment to boost customer spending.
The insights enable the marketing team to allocate budgets more efficiently for maximum return.