---
title: "Dataset Analysis Report"
author: "Yunhui Fan"
format:
  html:
    number-sections: true
    number-tables: true
    number-figures: true
  pdf:
    number-sections: true
    number-tables: true
    number-figures: true
---

# Load Libraries
```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
```

# Introduction
This report looks at customer data to understand shopping patterns.I want to see how visits and spending relate to how much customers buy.This can help make marketing decisions more effective.The findings will help explain what affects customer purchases.

# Research Question
I want to find out what affects how much customers spend on purchases.I will look at the number of visits and marketing spend for each customer.This report will show the relationship between these factors and purchase amount.

# Dataset Introduction
This dataset tracks customer behavior for an online store.It records each customer's marketing spend, site visits, and total purchase amount.It also includes customer segment information to group different types of shoppers.Before analysis, I removed rows with missing values and fixed inconsistent entries.This cleaned data ensures reliable results for the analysis.

```{r}
#| label: data-loading
#| echo: false
#| include: false

data <- read_csv("data/35036281_Yunhui Fan.csv")
data_clean <- data %>%
  drop_na() %>% 
  filter(purchase_amount >= 0)
```

## Dataset Description subsection
Dataset Description
This dataset has `r nrow(data_clean)` observations and `r ncol(data_clean)` variables.
The data includes numeric values like visits and purchase amount, and categorical groups like customer segment.
Table @tbl-data-cleaning shows the summary statistics for key numeric variables, and Figure @fig-purchaseplot displays the distribution of purchase amounts.

```{r}
#| label: tbl-data-cleaning
#| tbl-cap: "Summary of the dataset"
#| echo: false

data_clean %>%
  select(visits, marketing_spend, purchase_amount) %>%
  summary() %>%
  kable()
```

```{r}
#| label: fig-purchaseplot
#| fig-cap: "Distribution of customer purchase amounts."
#| echo: false
ggplot(data_clean, aes(x = purchase_amount)) +
  geom_histogram(fill = "steelblue", color = "white", bins = 15) +
  labs(x = "Purchase Amount (USD)", y = "Number of Customers")
```

## Results

This section looks at our research question: What factors influence customer purchase amounts?
As shown in Figure @fig-purchaseplot, most customers have relatively low purchase amounts. 
The distribution is right-skewed, meaning only a few customers spend very high amounts. 
The average purchase amount in this data is `r round(mean(data_clean$purchase_amount), 2)` USD.
Figure @fig-marketing-purchase shows a clear positive relationship between marketing spend and purchase amount. 
As marketing spend increases, customer purchase amounts tend to increase as well, showing a strong connection between marketing investment and customer spending.
Figure @fig-total-visits shows the distribution of customer visit counts. 
This bar chart helps us understand how often customers engage with the business, and we can see the most common number of visits clearly.
Together, these figures show that marketing spend and customer engagement both play important roles in influencing how much customers spend, which directly answers our research question.


```{r}
#| label: fig-marketing-purchase
#| fig-cap: "Marketing spend vs customer purchase amount"
#| echo: false

ggplot(data_clean, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point(color = "darkblue", alpha = 0.6) +
  geom_smooth(method = lm, se = FALSE, color = "red") +
  labs(
    x = "Marketing Spend (USD)",
    y = "Purchase Amount (USD)"
  )
```


```{r}
#| label: fig-total-visits
#| fig-cap: "Distribution of customer visit frequencies"
#| echo: false

ggplot(data_clean, aes(x = visits)) +
  geom_bar(fill = "darkred", color = "black") +
  labs(
    x = "Number of Visits",
    y = "Count of Customers"
  )
```

Conclusion
The analysis shows clear relationships between marketing spend, customer visits, and purchase amounts. Higher marketing spending is strongly associated with increased customer purchase amounts, demonstrating the effectiveness of marketing investment.
The distribution of purchase amounts indicates that most customers spend moderately, while a small group of high-value customers exists.
Visit patterns also show that general customer engagement is relatively consistent across the dataset.Overall, the findings support the idea that marketing efforts and customer engagement are key factors influencing customer spending behavior.
These insights can help guide future marketing strategies and improve business decisions.